\documentclass{resume}
\usepackage{tipa}

\title{Nicola Lamacchia - Résumé}
\author{Nicola Lamacchia}
\hypersetup{
    pdfsubject={Professional Experience, Education and Skills}
}
\footerinfo{
    \footnotesize\centerline{%
        Build %BuildHash%%
        \space\textemdash\space
        The source code of this résumé is available at
        \url{https://github.com/nicolalamacchia/resume}
    }
}

\begin{document}

\heading%
    {Nicola}
    {Lamacchia}
    {\textipa{/ni"k\textopeno\textlengthmark la la"mak.kja/}}
    {hire@nicola.dev}%
    {+39 327 651 4969}%
    {https://nicola.dev}
    {Milan, Italy}

\separator[cvlightgray]

\summary{%
    Passionate software engineer, with extensive experience on web
    application development and operations, software architecture and technical
    leadership. FOSS advocate. Embedded development and ML enthusiast.
}

\section{Professional Experience}

\begin{cvsection}
    \activity{Contractor}%
        {}%
        {May 2023}{Present}%
        {Remote}%
        {%
            \begin{itemize}
                \item Worked with several clients on web back end, front end
                    and infrastracture with several technologies, such as
                    Python, Go, Elixir, React, Svelte (SvelteKit), Next.js,
                    Remix, Terraform, Kubernetes.
                \item Supported data engineers on developing AI models (based
                    on GPT or self-hosted LLaMA) and helped them integrate
                    their solutions in the final products.
                \item Created cost-effective cloud solutions to host clients'
                    products using several cloud vendors (mostly AWS and GCP)
                    and bare metal providers.
            \end{itemize}
        }

    \activity{Technical Team Lead}%
        {Percona, LLC}%
        {Apr. 2021}{May 2023}%
        {Remote}%
        {%
            \begin{itemize}
                \item Led the Percona Portal team: mentoring and coaching
                    junior developers, encouraging them to embrace modern
                    practices and techniques, such as TDD and Continuous
                    Deployment, in order to provide high code quality and,
                    consequently, higher software quality.
                \item Fostered the adoption of the Empowered Product Teams
                    model within the team and the rest of the company, liaising
                    with the Product Manager and the Product Designer to
                    study solution feasibility, while contributing to the
                    overall product discovery and definition of functional
                    requirements.
                \item Engaged and worked closely with Product Designers to
                    define a design system and implemented an easily
                    customizeable theming system based on design tokens.
            \end{itemize}
        }

    \activity{Senior Software Engineer}%
        {Percona, LLC}%
        {Jun. 2020}{Mar. 2021}%
        {Remote}%
        {%
            \begin{itemize}
                \item Worked on Percona Monitoring and Management and then
                    participated to the creation of the new Percona SaaS
                    platform, in particular to what would later become
                    Percona Portal, by helping to define its architecture,
                    quality standards, CI/CD pipelines and to identify
                    non-functional requirements.
                \item Contributed to the front end architecture of Percona
                    Portal and to the creation of a UI library which was then
                    published as a public package (hosted on npm.js).
                \item Liaised with DevOps engineers, QA engineers and architects
                    to improve CI/CD pipelines and led the introduction of a
                    Continuous Deployment pipeline, starting from lower
                    environments.
            \end{itemize}
        }

    \activity{Senior Software Engineer}%
        {Dottori.it S.r.l.}%
        {Dec. 2019}{May 2020}%
        {Milan, IT}%
        {%
            \begin{itemize}
                \item Worked on the migration of a legacy PHP monolith to
                    microservices mostly written in Elixir/Phoenix, deployed to
                    a Kubernetes cluster hosted on Amazon AWS.
                \item Mentored front end junior developers and helped them to
                    move away from a monolithic front end, in favor of a Single
                    Page Application built with React.
            \end{itemize}
        }

    \activity{Senior Software Engineer}%
        {eBay, Inc.}%
        {Jan. 2018}{Aug. 2019}%
        {Milan, IT}%
        {%
            \begin{itemize}
                \item Front end representative for the architecture team.
                \item Facilitated the decomposition of a legacy monolith to
                    component-based, well tested and independently deployable
                    applications, using Back-end-For-Front-ends (BFFs) written
                    in Node.js and deployed in Continuous Delivery. The aim was
                    also to substantially improve observability and to reduce
                    friction in implementing service monitoring.
                \item Worked on the definition of a more modern architecture
                    with a strong focus on SEO, usability and performance,
                    following a mobile-first approach.
            \end{itemize}
        }

    \activity{Full Stack Engineer}%
        {Cloud Academy, Inc.}%
        {Jun. 2017}{Dec. 2017}%
        {Mendrisio, CH}%
        {%
            \begin{itemize}
                \item Worked on isomorphic React applications (with Redux to
                    manage the state and Redux-Saga to manage side effects),
                    using server-side rendering (with Next.js) and an atomic
                    architecture, with a Storybook-driven workflow. The
                    applications consumed RESTful APIs from the Python (Django)
                    back end.
            \end{itemize}
        }

    \activity{Full Stack Engineer}%
        {Ominee S.r.l.}%
        {Jan. 2015}{Jun. 2017}%
        {Turin, IT}%
        {%
            \begin{itemize}
                \item Led the development of the company's MVP, using a stack
                    based on Go, Flask (Python), Polymer, AngularJS, NoSQL
                    (MongoDB, Redis) and SQL databases.
                \item In charge of software architecture and operations,
                    encouraging and implementing a DevOps approach.
            \end{itemize}
        }

    \activity{Mentor and Evangelist (pro bono)}%
        {Puglia SOS}%
        {2013}{Present}%
        {Barletta, IT}%
        {%
            \begin{itemize}
                \item In charge of events organization (such as Linux Day) for
                    the NPO Puglia Software Open Source.
                \item Mentored high school aged students in a programming course
                    called CodingLab.
            \end{itemize}
        }

    \activity{Software Engineer}%
        {Canoe ERP}%
        {2013}{2014}%
        {Barletta, IT}%
        {%
            \begin{itemize}
                \item Led the design process for a web application with the goal
                    of creating an easily customizable suite to manage and
                    improve the productivity of teams in small and medium-sized
                    businesses. The application was based on the full MEAN
                    stack and was cloud-hosted.
            \end{itemize}
        }

    \activity{Freelance Developer}%
        {}%
        {2010}{2013}%
        {}{}
\end{cvsection}

\section{Education}

\begin{cvsection}
    \activity{Electronic Engineering}{Università degli Studi Roma Tre}%
        {2007}{2011 \lbrack \textit{interrupted}\rbrack}{Rome, IT}{}
\end{cvsection}

\section{Languages}

\begin{languagessection}
    \lang{Italian}{native language}
    \lang{English}{full professional proficiency}
\end{languagessection}

\section{Skills / Keywords}

\begin{skillssection}
    \skills{Programming and Markup Languages}%
        {Python, JavaScript, TypeScript, Go, Elixir, PHP, C/C++; Shell
            scripting (Bash, Zsh, POSIX shells: ash, dash);\\%
            x86-64, ARM and 6502 assembly;\\%
            XHTML, HTML5, CSS3, SASS, LESS, Stylus;}

    \skills{Frameworks and Libraries}%
        {Flask, Node.js, Express, Phoenix, Vue.js, React, React Native, Svelte,
            Redux, Web Components, Celery, NLTK, NumPy, pandas, Matplotlib,
            D3.js, Storybook;\\%
            front end workflow: task runners, package managers, webpack,
            etc.;\\%
            testing: py.test, tox, Jest, et al.; end2end testing.}

    \skills{Databases}%
        {RDBMS: MySQL, MariaDB, PostgreSQL, SQLite;\\%
            NoSQL: MongoDB, CouchDB.}

    \skills{Message Brokers}%
        {RabbitMQ, ZeroMQ, Kafka.}

    \skills{Cache Systems and Web Accelerators}%
        {Redis, Memcached, Varnish.}

    \skills{Version Control Systems}%
        {Git, Mercurial, Subversion.}

    \skills{Development Methodologies}%
        {Scrum, Kanban, XP, TDD/BDD, DDD, design patterns, CI/CD, CQRS, Event
            Sourcing, Evolutionary Architectures;\\%
            Web apps: Atomic Design, Progressive Web Apps (PWAs);\\%
            CSS: BEM, SMACSS.}

    \skills{DevOps/Cloud}%
        {Docker, Vagrant, Ansible, Jenkins, Kubernetes, Terraform, AWS,
            Cloudflare;\\%
            Monitoring systems and dashboards: Prometheus, Elastic stack,
            Grafana.}

    \skills{Operating Systems and Networking}%
        {GNU/Linux and *BSD system administration and networking;\\%
            Knowledge of the ISO/OSI stack and networking RFCs.}

    \skills{Product Management and Design Tools}%
        {InVision, Figma, Sketch, Canva, Balsamiq, Zeplin, Miro, Jira, Trello,
            Confluence.}
\end{skillssection}

\end{document}
